Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2015-01-13 paper/sheaf_lics.tex
abstract of sheaf_lics.pdf

\documentclass[conference]{IEEEtran}
% *** MATH PACKAGES ***
%
\usepackage[cmex10]{amsmath}
\usepackage{amssymb,amsthm,amsfonts}

@@

@@

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Sheafification in HoTT}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Kevin Quirin and Nicolas Tabareau}
\IEEEauthorblockA{INRIA \\ \'Ecole des Mines de Nantes \\ Nantes, France}}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Abstract
\end{abstract}

@@

@@

@@

>>>>

\documentclass[conference]{IEEEtran}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

% *** MATH PACKAGES ***
%
\usepackage[cmex10]{amsmath}
\usepackage{amssymb,amsthm,amsfonts}

@@

\newcommand{\mynote}[2]{
    \fbox{\bfseries\sffamily\scriptsize#1}
    {\small$\blacktriangleright$\textsf{\emph{#2}}$\blacktriangleleft$}~}

\newcommand\kq[1]{\mynote{KQ}{#1}}
\newcommand\nt[1]{\mynote{NT}{#1}}

@@

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Lawvere-Tierney Sheafification\\ in Homotopy Type Theory}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Kevin Quirin and Nicolas Tabareau}
\IEEEauthorblockA{Inria \\ \'Ecole des Mines de Nantes \\ Nantes, France}}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}

  Sheafification is a popular tool in (higher) topos theory which
  allows to extend the internal logic of a topos with new
  principles. One of the most famous applications is the possibility to
  transform a topos into a boolean topos using the dense topology, which
  corresponds in essence to Gödel's double negation translation. 
  % 
  The same construction has not been considered in Martin-Löf type
  theory because of a mismatch between topos and type theory. This
  mismatched has been fixed recently by considering homotopy type
  theory, an extension of Martin-Löf type theory with new
  principles inspired by category theory and homotopy theory.
  % 
  In this paper, we give a computer checked construction of
  Lawvere-Tierney sheafification in homotopy type theory, which allows
  in particular to give a meaning to the (propositional) law of
  excluded middle inside homotopy type theory, without axiom.

\end{abstract}

@@

\begin{itemize}
\item 
  links between HoTT and higher topos theory 
\item 
  modalities in HoTT
\item 
  Giraud's axiom
\item
  previous attempts to extend Gödel's double negation to 
  Martin-Löf type theory
\item 
  compare to the work of Parigot on $\lambda\mu$-calculus (Classical proofs as programs), and Coquand 
  (A realization of the negative interpretation of the Axiom of
  Choice)
\item
  work of Hugo Herbelin, A Constructive Proof of Dependent Choice,
  Compatible with Classical Logic
\item
  Barthe (CPS Translating Inductive and Coinductive Types)
  ``No translation is possible along the same lines for small $\Sigma$-types
  and sum types with dependent case.''
\item

\end{itemize}

@@

\nt{
  Il faut au minimum introduire proprement les n-Types, le squash
  sur les props 
}

@@

\nt{
To be checked:
  Condition iv of Thm 7.7.5 of HoTT
}
